---
title: "An Analysis On Financial Complaints"
description: |
  Financial complaints broken down by the top states.
author:
  - name: Morgan Miller
    url: https://www.google.com
date: 04-13-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(kableExtra)
library(htmlwidgets)
library(htmltools)
library(readxl)

complaints <- readRDS("complaints.rds")


```

Below find my analysis on financial complaints broken down by the top 5 states.

I began this analysis by downloading the data of financial complaints and selecting the data I wanted to analyze. I used the code:

topic <- select(complaints, sub_product)

topics_summed <- count(topic, sub_product)

```{r}

topic <- select(complaints, sub_product)

topics_summed <- count(topic, sub_product)

topics_summed
```
I then sorted the complaints by states and counted them up using the following code 

state_complaints <- select(complaints, c(state, product))

state_summed <- count(state_complaints, state)

```{r}
state_complaints <- select(complaints, c(state, product))

state_summed <- count(state_complaints, state)

state_summed

```

Finally, I placed the data in a plotly bar graph code and created the following bar graph with the top 5 states with the most financial complaints according to my data.

```{r}
graph1 <- plot_ly(
  x = c("FL", "CA", "TX", "NY", "GA"),
  y = c(50449, 46721, 44504, 25445, 23881),
  type = "bar",
  color = "orange"
)

graph1
```

