---
title: "An Analysis On Campaign Events By Morgan Miller"
description: |
  Kamala Harris visits on the 2020 campaign trail.
author:
  - name: Morgan Miller
    url: https://www.google.com
date: 04-13-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(plotly)

events <- readRDS("events_saved.rds")

```

Below find my analysis on the visits per month by Kamala Harris on the presidential campaign trail in 2020.

I began with a layout of all visits by each candidate in the 2020 primaries.

```{r}

head(events)

```

I then sorted the months by the last name "Harris" using the code below. In additon, I gave the count command to tally up all visits during that month (shown under the "n" column in "kamala_months"). I used the code:

events_month <- events%>%
  mutate(month(date))

Kamala_months <- events_month%>%
  filter(cand_lastname == "Harris")%>%
  count(month = month(date))

```{r}

events_month <- events%>%
  mutate(month(date))

Kamala_months <- events_month%>%
  filter(cand_lastname == "Harris")%>%
  count(month = month(date))

Kamala_months


```

Finally, I created a bar graph which illustrated the month and number of time visited by Harris during the 2020 presidential campaign trail.

```{r}

Harris_Chart <- Kamala_months%>%
  plot_ly(x = ~month,
          y = ~n, 
          type = "bar")

harris_graph <- Harris_Chart%>%
  layout(title = "Visits for Harris per Month")

harris_graph

```
